Spatiotemporal Data Classification

### 2018-01-06 Report/BigDataHomeworkPandas.tex
update report, update dependecies

	\todo{paralization}

	In this function, the 3rd column of the dataframe is providing and it is transformed in tuples with the latitudes and longitudes. The list nearest neighbours will keep in tuples for each train trip the trip\_id, the calculated distance (which is calculated using the dynamic time wraping algorithm), the journeyId and finally all the points of the journey. 
	\todo{custom algorithm or library}

@@

>>>>

	There are three ways to execute this task: using processes, threads or serial execution. This information is provided as input giving the kind of execution and the number of processes/threads as well. In the function run\_with\_processes an async task is executed for each process and then the result is stored in a list, while in the function run\_with\_threads the dataframe is splitted in sub dataframes (the number is specified by the number of threads) and then distance is calculated for each subdataframe. After thread join, the result is also stored in the nearest\_neighbours list.

	In the function calculate\_dists, the 3rd column of the dataframe is provided and it is transformed in tuples with the latitudes and longitudes. The list nearest neighbours will keep in tuples for each train trip the trip\_id, the calculated distance (which is calculated using the dynamic time wraping algorithm), the journeyId and finally all the points of the journey.

	\todo{custom algorithm or library}

@@

	Below, there is an example of the 6 produced maps, showing the nearest sub-routes related to a test trip:

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.50] {question2a1example.jpg}
			\caption{Example of nearest sub-routes trips visualization}
		\end{center}
	\end{figure}
